Detecting changes in dispersion in COVID-19 incidence time series using a negative binomial model

### 2023-05-20 noise_covid_v2.Rmd
edit visualization for significant counties

```{r, fig.cap = "P-values resulting from testing whether the dispersion parameter is smaller after Thanksgiving in each county in New York (Wald)"}
par(mfrow = c(1,2))
state <- "NY"
source("code/wald_counties.R")

state <- "FL"
source("code/wald_counties.R")
```
```{r}
library(tigris)
fl <- counties("Florida")
load("data/W_pvalsFL.Rdata")
p <- round(pvals, digits=1)
p[is.na(p)] <- "na"
fl$p <- p

@@

```{r, fig.cap = "P-values resulting from testing whether the dispersion parameter is smaller after Thanksgiving in each county in New York (LRT)"}
par(mfrow = c(1,2))
state <- "NY"
source("code/lrt_counties.R")
NY_sig <- (which(pvals < 0.05))

state <- "FL"
source("code/lrt_counties.R")
FL_sig <- (which(pvals < 0.05))
```
Note that in these visualizations, an NB2 fit would be:
A Poisson fit would be:
```{r}
signif_index <- c(NY_sig, FL_sig)

state <- "NY"
source("code/squared.res_v_squared.fitted.R")

state <- "FL"
source("code/squared.res_v_squared.fitted.R")

source("code/vis_signific_state.R")
```

@@

```{r}
load("data/pvals_sim_Wald.Rdata")
mean(pvals[which(curve_parms$theta1==curve_parms$theta2)], col=1)
mean(pvals[which(curve_parms$theta1!=curve_parms$theta2)], col=2)

load("data/pvals_sim_LRT.Rdata")
mean(pvals[which(curve_parms$theta1==curve_parms$theta2)], col=1)
mean(pvals[which(curve_parms$theta1!=curve_parms$theta2)], col=2)

```

>>>>

```{r, fig.cap = "P-values resulting from testing whether the dispersion parameter is smaller after Thanksgiving in each county in New York (Wald)"}
par(mfrow = c(1,2))
state <- "NY"
source("code/wald_counties.R")
signif_index <- state_index[(which(pvals < 0.05))]
source("code/squared.res_v_squared.fitted.R")
source("code/vis_signific_state.R")

state <- "FL"
source("code/wald_counties.R")
```

```{r, fig.cap = "P-values resulting from testing whether the dispersion parameter is smaller after Thanksgiving in each county in New York (LRT)"}
par(mfrow = c(1,2))
state <- "NY"
source("code/lrt_counties.R")

state <- "FL"
source("code/lrt_counties.R")
```

```{r}
library(tigris)
fl <- counties("Florida")
load("data/W_pvalsFL.Rdata")
p <- round(pvals, digits=1)
p[is.na(p)] <- "na"
fl$p <- p

@@

Note that in these visualizations to check the relationship between mean and dispersion, an NB2 fit would be:
A Poisson fit would be:

@@

```{r}
load("data/pvals_sim_Wald.Rdata")
mean(pvals[which(curve_parms$theta1 == curve_parms$theta2)] < 0.05)
mean(pvals[which(curve_parms$theta1 != curve_parms$theta2)] < 0.05)

load("data/pvals_sim_LRT.Rdata")
mean(pvals[which(curve_parms$theta1==curve_parms$theta2)] < 0.05)
mean(pvals[which(curve_parms$theta1!=curve_parms$theta2)] < 0.05)
```
